\begin{thebibliography}{9}
\bibitem{Boudot}
Fabrice Boudot. “Efficient Proofs that a Committed Number Lies in an Interval”, n.d. https://www.iacr.org/archive/eurocrypt2000/1807/18070437-new.pdf. 

\bibitem{Survey}
Eduardo Morais, Tommy Koens, Cees van Wijk, and Aleksei Koren. “A Survey on Zero Knowledge Range Proofs and Applications - SN Applied Sciences.” SpringerLink, July 31, 2019. https://link.springer.com/article/10.1007/s42452-019-0989-z. 

\bibitem{Sharp}
Geoffroy Couteau, Dahmun Goudarzi, Michael Klooß, and Michael Reichle. “Sharp: Proceedings of the 2022 ACM SIGSAC Conference on Computer and Communications Security.” ACM Conferences, November 1, 2022. https://dl.acm.org/doi/10.1145/3548606.3560628. 

\bibitem{Maths}
Johann Engelbrecht, Salvador Llinares, and Marcelo C. Borba. “Transformation of the Mathematics Classroom with the Internet - ZDM – Mathematics Education.” SpringerLink, June 26, 2020. https://link.springer.com/article/10.1007/s11858-020-01176-4. 

\bibitem{Maths2}
Pranathi Rayavaram, Sreekriti Sista, Ashwin Jagadeesha, Justin Marwad, Nathan Percival, Sashank Narain, and Claire Seungeun Lee. “Designing a Visual Cryptography Curriculum for K-12 Education.” IEEE, February 22, 2023. https://ieeexplore.ieee.org/abstract/document/10125191. 

\bibitem{Ball}
0xSage. “Understanding Zero-Knowledge Proofs through Simple Examples.” Medium, May 12, 2019. https://blog.goodaudience.com/understanding-zero-knowledge-proofs-through-simple-examples-df673f796d99.  

\bibitem{Mexico}
Lupita. “Genuino Cloud: Correo Electrónico Corporativo.” Genuino Cloud | Correo electrónico corporativo, December 6, 2020. https://genuinocloud.com/blog/3-consejos-para-proteger-tu-identidad-en-internet/. 

\bibitem{Fraudes}
Katherine Skiba. “Se Disparan Los Fraudes En Instragram Por La Pandemia.” AARP, November 4, 2020. https://www.aarp.org/espanol/dinero/estafas-y-fraudes/info-2020/se-disparan-los-enganos-en-redes-sociales-por-pandemia.html. 

\bibitem{zCash}
Electric Coin Company. “Zcash Privacy Remains Strongest of Any Cryptocurrency, Even with Recent Chainalysis, Elliptic Support.” Electric Coin Company, September 23, 2020. https://electriccoin.co/blog/zcash-privacy-remains-strongest-of-any-cryptocurrency/. 

\bibitem{Monero}
Jana Kane. “Monero (XMR) Price Prediction for 2023, 2024-2025 and Beyond.” LiteFinance, January 9, 2023. https://www.litefinance.org/blog/analysts-opinions/monero-price-prediction-forecast/. 

\bibitem{Motivacion}
Juan Fornell. “¿Qué Es Zero Knowledge Protocol (ZKP)?” Bit2Me Academy, May 4, 2023. https://academy.bit2me.com/zkp-zero-knowledge-protocol/.

\bibitem{Historia}
Shafi Goldwasser, Silvio Micali, and Charles Rackoff. “The Knowledge Complexity of Interactive Proof-Systems”, February 1989. https://people.csail.mit.edu/silvio/Selected\%20Scientific%20Papers/Proof%20Systems/Computationally_Sound_Proofs.pdf. 

\bibitem{ZKP}
Karim Baghery. “CO6GC: Introduction to Zero-Knowledge Proofs (Part 1).” COSIC, June 8, 2022. https://www.esat.kuleuven.be/cosic/blog/co6gc-introduction-to-zero-knowledge-proofs-1/. 

\bibitem{zk-STARKs vs zk-SNARKs}
Cointelegraph Research. “Pushing Bitcoin to Become More Scalable with Zero-Knowledge Proofs.” Cointelegraph, August 17, 2022. https://cointelegraph.com/news/pushing-bitcoin-to-become-more-scalable-with-zero-knowledge-proofs. 

\bibitem{Comparacion}
Paul Razvan. “ZK-SNARKs vs. ZK-Starks vs. BulletProofs? (Updated).” Ethereum Stack Exchange, March 5, 2019. https://ethereum.stackexchange.com/questions/59145/zk-snarks-vs-zk-starks-vs-bulletproofs-updated. 

\bibitem{Definiciones}
“Zero-Knowledge Proofs.” ethereum.org, n.d. https://ethereum.org/en/zero-knowledge-proofs/. 

\bibitem{Bulletproofs}
Cathie Yun. “Building on Bulletproofs.” Medium, July 11, 2021. https://cathieyun.medium.com/building-on-bulletproofs-2faa58af0ba8. 

\bibitem{Bulletproofs2}
Benedikt Bünz, Jonathan Bootle, Dan Boneh, Andrew Poelstra, Pieter Wuille, and Greg Maxwell. “Bulletproofs: Short proofs for confidential transactions and more”, n.d. https://eprint.iacr.org/2017/1066.pdf. 

\bibitem{MapToGroup}
Boneh, Dan, Ben Lynn, and Hovav Shacham. “Short Signatures from the Weil Pairing.” SpringerLink, November 20, 2001. https://link.springer.com/chapter/10.1007/3-540-45682-1\_30. 

\bibitem{Curvas}
Brown, Daniel R. L. “Sec 2: Recommended elliptic curve domain parameters.” January 27, 2010. https://www.secg.org/sec2-v2.pdf.

\bibitem{Curvas2}
“Elliptic Curve Cryptography (ECC).” Elliptic Curve Cryptography (ECC) - Practical Cryptography for Developers, n.d. https://cryptobook.nakov.com/asymmetric-key-ciphers/elliptic-curve-cryptography-ecc. 

\bibitem{Pedersen}
Torben Pryds Pedersen. “Non-Interactive and Information-Theoretic Secure Verifiable Secret Sharing.” SpringerLink, 1992. https://link.springer.com/chapter/10.1007/3-540-46766-1\_9. 

\bibitem{Wikipedia}
“Zero-Knowledge Proof.” Wikipedia, May 27, 2023. https://en.wikipedia.org/wiki/Zero-knowledge\_proof. 

\bibitem{MD5}
“MD5 Hash: Generate MD5 Message Digests Online.” cryptii, n.d. https://cryptii.com/pipes/md5-hash. 

\bibitem{ganttproject}
BarD Software s.r.o. “Free Project Management Tool for Windows, Macos and Linux.” GanttProject, n.d. https://www.ganttproject.biz/. 

\bibitem{AES}
“AES Animation.” CrypTool Portal, n.d. https://www.cryptool.org/en/cto/aes-animation. 

\bibitem{Bulma}
“Free, Open Source, and Modern CSS Framework Based on Flexbox.” Bulma, n.d. https://bulma.io/.
\end{thebibliography}